Target Readability in Interpersonal Accuracy

### 2022-05-16 manuscript.Rmd
descriptives and personality

map_dbl(descriptive_df, mean, na.rm = TRUE)
map_dbl(descriptive_df, sd, na.rm = TRUE)

get_descrip(descriptive_df, Extr)

```
Table 1 represents descriptive statistics for all the variables in the present study.

```{r}
# personality traits
samdata <- import(here("data", "samdata.csv"))

SAM1 <- lmer (ptrait ~ targSRrC + AvgtraitC + (targSRrC + AvgtraitC |PerUn) + (targSRrC + AvgtraitC |TarUn) + (targSRrC + AvgtraitC |DyUn), data=samdata)

summary (SAM1)

@@

>>>>

table1 <-
tibble(
  var = names(descriptive_df),
  mean = map_dbl(descriptive_df, mean, na.rm = TRUE),
  sd = map_dbl(descriptive_df, sd, na.rm = TRUE)
)
```
Table 1 represents descriptive statistics for all the variables in the present study.

```{r}
table1
```

```{r}
# personality
samdata <- rio::import(here::here("data", "samdata.csv"))

samdata <-
  samdata %>% 
  mutate(

    Avgtrait = Avgtrait - 1,
    targSRr = targSR - Avgtrait,

    # Note to self: use a loop for these.
    targSRrC = scale(targSRr, scale = FALSE, center = TRUE),
    AvgtraitC = scale(Avgtrait, scale = FALSE, center = TRUE),
    ptraitC = scale(ptrait, scale = FALSE, center = TRUE)
  )

## null model
null1 <- lmer (ptrait ~ (1|PerUn) + (1|TarUn) + (1|DyUn) + (1|Group), 
               data = samdata)

sjPlot::tab_model(null1)
```

@@

```{r}
# personality
## final model
SAM1 <- lmer(ptrait ~ targSRrC + AvgtraitC + 
                (1 | PerUn) + 
                (1 | TarUn) + 
                (1 | DyUn), 
              data = samdata)

summary(SAM1)
(SAM1)

## fit a model for each perceiver
models_dyad <- 
samdata %>% 
  group_by(PerUn) %>% 
  nest() %>% 
  mutate(models = map(data, ~ {

    lm(ptrait ~ targSRrC + AvgtraitC, 
              data = .x)

  }
                      )
         )
```
